Usable Security in Virtual Power Plants

### 2018-01-17 acmart-master/draft.tex
Added VPP info and Inference

\section{Security in Critical Infrastructure}

@@

Virtual Power Plant(VPP) is one such infrastructure. A VPP is centralized system that aggregates various energy sources to meet the energy demand of a geographical area. It relies upon software to remotely control, optimize and dispatch Distributed Energy resources(DERs). At the heart of every VPP is the Energy Management System(EMS). The EMS manages power flows in order to minimize the electricity generation costs and avoid loss of energy produced by generators based on renewable energy sources.

As a result, there may be new and unprecedented attacks on smart grids, including those that exploit zero-day vulnerabilities. Therefore, in such cases when the system is under attack and needs to be controlled by the operator, an existing authentication system(i.e, the existing security mechanism in place), must be usable under stress. Traditional authentication mechanisms are largely based on password based systems. Having a long random password is good advice. It provides a measure of security for guarding access to important information, such as your online banking account. 
Unfortunately, when faced with having to remember several random fifteen character passwords (characters being A to Z, a to z, 0 to 9 and an assortment of other printable characters such as ! @ \# \$ and \%), most users apply a judgement to the value of the information protected by the password and act accordingly.\\
Some accounts may have a relatively weak password, because of the cost of undue information leakage or harm to the owner if the account is compromised. Other accounts might have a stronger password because users don't want their money siphoned off by a cyber-criminal. These are judgements about the perceived value of the information. \\
Passwords are also exceptionally susceptible to dictionary and brute force attacks. Simple passwords can be cracked in seconds and longer passwords that include common words and phrases from literature take up to a week to be cracked. Passwords can be called secure if the time required to crack is sufficiently long, such as in years or decades. Such passwords may be constructed from a combination of alphabets, numbers and symbols. There is a trade off though, as such passwords are harder to remember and also hard to enter into a system without errors. It is also compounded by the fact that users are recommended to change passwords periodically. This invites a lot of pressure onto users who are not technologically friendly and are oblivious to the system structure. Additionally, in certain circumstances, such as an emergency situation, a user may need quick access to resources. In such a situation, a user is more likely to make mistakes entering a complicated password and being denied access. If the user is an operator of a smart grid, this could lead to a catastrophe. Therefore, the most secure passwords are, in fact, the least usable.

@@

Therefore, a \textit{usable security framework for an authentication system} consists of an authentication system which includes a user-friendly interface, requires a user to have little to no authentication tokens, satisfies the criteria for a conventional security system such as Confidentiality, Integrity and Availability in addition to all the criteria mentioned above. The evaluation of these criteria with respect to their metrics should fall in the permissible zone. The user also must provide feedback and specify the drawbacks, if any and suggestions to improve the system from the perspective of usability.

@@

\subsection{Validation}
To demonstrate how this framework could be used, we use an example. Two different authentication systems were tested, a fingerprint matching system and a simple password system. The evaluation involved participants using both types of systems and then answering a questionnaire. To assess fingerprint matching, two approaches were used. Since, there are several types of fingerprint matching algorithms, performance may vary. Therefore the most common implementations found in real life was used. First, an optical scanner of fingerprints was evaluated. An optical scanner scans the fingerprint into an optical image and compares the image as is with a database of images. This process is slow and less secure, as images of fingerprints are stored unprotected in the database. The second kind was a capacitive scanner, where fingerprints are read using varying electric charges when a ridge comes in contact with the scanner. This change is charge is converted to digital data, which is then analysed to look for unique features. Data is stored digitally, though not necessarily encrypted. This form of storing data is still vulnerable but more secure than images. There were 30 participants whose fingerprints were added to a database of more than 1000 entries. The results of the capacitive scanner were found to be more optimal. They are shown below:

\begin{center}
\begin{table}[H]
\caption{Results for Biometric systems.}
\label{tab:result2}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|}
\hline
\textbf{Security Metric} & \textbf{Observed values} \\
\hline
EER & 3.9\%\\
\hline
Accuracy (Success Rate of Correct Input) & 96.1\%. \\
\hline
Task Completion Time & Average of 1.8 seconds \\
\hline
Interface Design & 4.2\\
\hline
Memory Load & 5\\
\hline
\end{tabular}
}
\end{table}
\end{center}

@@

\begin{center}
\begin{table}[H]
\caption{Inference Table for password based systems.}
\label{tab:infer_password}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|c|}
\hline
\textbf{Security Metric} & \textbf{Expected values} & \textbf{Observed values} \\
\hline
Accuracy (Success Rate of Correct Input) & 100\% & 100\%. \\
\hline
Task Completion Time & 10-12 seconds & Avg of 12.2 seconds \\
\hline
Interface Design & >4 & 4.7\\
\hline
Memory Load & >4 & 3.5\\
\hline
\end{tabular}
}
\end{table}
\end{center}

Interface Design and Memory Load were scored with the same method as for biometric systems. Interface design received a higher score due to the familiarity to users, however due to complicated passwords, it was harder to remember multiple difficult and complex passwords for various systems simultaneously. It also affected the task completion time, which was relatively longer. Accuracy is 100\% since a correctly entered password was never rejected. We are not counting mistyped passwords. A reason for this is, the measure used for biometrics is accuracy. In biometric systems fingerprints are rarely falsely entered, although a possibility. Users are aware of which fingerprint is required. Therefore, in fingerprint systems accuracy of the algorithm is used as a measure for the performance. To keep the consistency, accuracy was used for password systems.

\subsection{Inference}

>>>>

\section{Security in Virtual Power Plants}

@@

Virtual Power Plant(VPP) is one such infrastructure. A VPP is a centralized system that aggregates various energy sources to meet the energy demand of a geographical area. It relies upon software to remotely control, optimize and dispatch energy from Distributed Energy resources(DERs). At the heart of every VPP is the Energy Management System(EMS). The EMS manages power flows in order to minimize the electricity generation costs and avoid loss of energy produced by generators based on renewable energy sources. The EMS consists of a set of software programs designed to control and monitor several aspects of the power plant such as generation levels, capacity, current and voltage levels, power fluctuations, supply-demand matching and so on. These software programs are automated and carry out operations based on pre-defined rules and functions. They are consistently monitored by an operator, known as VPP Operator. Therefore, a VPP is a system that employs software and networking tools making it susceptible to cyber attacks. There are several known ways to attack a power plant, network based attacks such as man-in-the-middle, Masquerading, Spoofing, Denial of service, Injection etc, software vulnerability based attacks, hardware based attacks and so on. Most of the known attacks have defined countermeasures which are in use to protect the power plant. Even with the presence of an extensive defense infrastructure, there may be new and unprecedented attacks on power plants, including those that exploit zero-day vulnerabilities. 
\newline
A virtual power plant under attack is expected to continue functioning normally, i.e, it must primarily meet the goal of energy supply to the customer end. In anticipation of such attacks, the system may be configured to reschedule, find replacement sources or even attempt to control the system to prevent its shutdown or damage. The operator may be requested to control the system in case of unprecedented events or cases where the operator's intervention and authorization are required. For example, consider a scenario when a power plant is under attack and its primary generation units are inaccessible. The VPP then attempts to find replacement units. However, in case of a large scale attack units in the neighbourhood may also be rendered inaccessible. Therefore, the VPP may have to look for units outside its allotted area which may require operator request and authorization. In such a case, the operator is required to access and operate the system. We assume there is an authentication mechanism in place that protects the system from unauthorized access, and therefore is the first interface the operator comes across. This authentication interface is vital since it prevents unauthorized personnel from accessing the system either in normal system state or when the system is under attack, which could be orchestrated by the unauthorized personnel themselves. The authentication mechanism should however be a usable mechanism, even under stress, to prevent the legitimate power plant operator from being locked out.

Traditional authentication mechanisms are largely based on password based systems. Having a long random password is good advice. It provides a measure of security for guarding access to important information, such as your online banking account. 
Unfortunately, when faced with having to remember several random fifteen character passwords (characters being A to Z, a to z, 0 to 9 and an assortment of other printable characters such as ! @ \# \$ and \%), most users apply a judgement to the value of the information protected by the password and act accordingly.\\
Some accounts may have a relatively weak password, because of the cost of undue information leakage or harm to the owner if the account is compromised. Other accounts might have a stronger password because users don't want their money siphoned off by a cyber-criminal. These are judgements about the perceived value of the information. \\
Passwords are also exceptionally susceptible to dictionary and brute force attacks. Simple passwords can be cracked in seconds and longer passwords that include common words and phrases from literature take up to a week to be cracked. Passwords can be called secure if the time required to crack is sufficiently long, such as in years or decades. Such passwords may be constructed from a combination of alphabets, numbers and symbols. There is a trade off though, as such passwords are harder to remember and also hard to enter into a system without errors. It is also compounded by the fact that users are recommended to change passwords periodically. This invites a lot of pressure onto users who are not technologically friendly and are oblivious to the system structure. Additionally, in certain circumstances, such as an emergency situation, a user may need quick access to resources. In such a situation, a user is more likely to make mistakes entering a complicated password and being denied access. If the user is an operator of a power plant, this could lead to a catastrophe. Therefore, the most secure passwords are, in fact, the least usable.

@@

Therefore, a \textit{usable security framework for an authentication system} consists of an authentication system which includes a user-friendly interface, requires a user to have minimalistic or easy to use authentication tokens, satisfies the criteria for a conventional security system such as Confidentiality, Integrity and Availability in addition to all the usability factors mentioned in \ref{tab:security-usability-relation}. The evaluation of these factors via usability criteria with respect to their metrics should fall in the permissible zone. The user also must provide feedback and specify the drawbacks, if any and suggestions to improve the system from the perspective of usability.

@@

\subsection{Validation}
To demonstrate how this framework could be used, we use an example. Two different authentication systems were tested, a fingerprint matching system and a simple password system. The evaluation involved participants using both types of systems and then answering a questionnaire. To assess fingerprint matching, two approaches were used. Since there are several types of fingerprint matching algorithms, performance may vary. Therefore, the most common implementations found in real life were used. First, an optical scanner of fingerprints was evaluated. An optical scanner scans the fingerprint into an optical image and compares the image as is with a database of images. This process is slow and less secure, as images of fingerprints are stored unprotected in the database. The second kind was a capacitive scanner, where fingerprints are read using varying electric charges when a ridge comes in contact with the scanner. This change is charge is converted to digital data, which is then analysed to look for unique features. Data is stored digitally, though not necessarily encrypted. This form of storing data is still vulnerable but more secure than images. There were 30 participants whose fingerprints were added to a database of more than 1000 entries. The results of the capacitive scanner were found to be more optimal. They are shown below:

\begin{center}
\begin{table}[H]
\caption{Results for Biometric systems.}
\label{tab:result1}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|}
\hline
\textbf{Security Metric} & \textbf{Observed values} \\
\hline
EER & 3.9\%\\
\hline
Accuracy (Success Rate of Correct Input) & 96.1\%. \\
\hline
Task Completion Time & Average of 1.8 seconds \\
\hline
Interface Design & 4.2\\
\hline
Memory Load & 5\\
\hline
\end{tabular}
}
\end{table}
\end{center}

@@

\begin{center}
\begin{table}[H]
\caption{Results for password based systems.}
\label{tab:result2}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|c|}
\hline
\textbf{Security Metric} & \textbf{Expected values} & \textbf{Observed values} \\
\hline
Accuracy (Success Rate of Correct Input) & 100\% & 100\%. \\
\hline
Task Completion Time & 10-12 seconds & Avg of 12.2 seconds \\
\hline
Interface Design & >4 & 4.7\\
\hline
Memory Load & >4 & 3.5\\
\hline
\end{tabular}
}
\end{table}
\end{center}

Interface Design and Memory Load were scored with the same method as for biometric systems. Interface design received a higher score due to the familiarity to users, however due to complicated passwords, it was harder to remember multiple difficult and complex passwords for various systems simultaneously. It also affected the task completion time, which was relatively longer. Accuracy is 100\% since a correctly entered password was never rejected. We are not counting mistyped passwords. A reason for using accuracy is that the measure used for biometrics is accuracy. In biometric systems fingerprints are rarely falsely entered, although a possibility. Users are aware of which fingerprint is required. Therefore, in fingerprint systems accuracy of the algorithm is used as a measure for the performance. To keep the consistency, accuracy was used for password systems, even though accuracy is normally not a measure for such systems. A correctly entered password will never be rejected, provided the credentials exist and are legitimate.

\subsection{Inference}
Now that we have results of two different authentication systems, a comparison can be made to assess which is more usable of the two. Tables \ref{tab:result1} and \ref{tab:result2} can be compared now that they have normalized metrics, i.e, common metrics. Since the EER is only used in biometric cases, it will not be used for comparison. Password based systems have a 100\% accuracy and a high rating for "Interface Design", but as explained earlier, these values were expected. Accuracy of biometric system observed as 96.1\% is still formidable. In case of a false negative, the task completion time, being exceptionally low, compensates for the time lost. The key factors are Task Completion Time, Interface Design and Memory Load. The fingerprint matching system used was exceptionally fast at 1.8 seconds for a successful authentication, although this can be attributed to relatively low sample space and the user of a capacitive scanner. In contrast a password system took an average of 12.2 seconds. This may be due to complexity of passwords, typing speed and additional time required to enter the user identifier such as a username. Interface design were both scored above 4, with password systems higher due to its familiarity to users. Memory Load, being a very important focus, due to difficulty in remembering difficult passwords especially under stress, shows that password systems are not preferable at all. Fingerprint systems require no memory use and are very usable.\\
It can be seen from the comparison that biometric systems such as fingerprint recognition and matching systems are accurate, faster, easy-to-use and are hence very usable.

### 2018-01-17 acmart-master/sample-sigconf-authordraft.tex
Added VPP info and Inference

\begin{document}
\title{Usable Security in Smart Grid Environment}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as  \texttt{acmart.pdf} document}

@@

\begin{abstract}
Automation of systems requires users to be less involved in system control. During situations when a user must control the system manually, the technology available must assist the user to complete their task and must not be a hindrance. Therefore, it is necessary to make the system more usable. Usability is often overlooked in favour of primary system goals, hence the lack of advancement in the usability drive. There exists no concrete framework to assess usability of a system, since most existing approaches focus on user feedback and neglect system optimization. In this study, usability is described in context of security in critical infrastructure. A usability framework was established for authentication mechanisms. It was determined that usability arises by optimizing system factors that relate to usability standards with the crucial addition of user preferences. Additionally, the approach can be applied to any target system to assess usability.
\end{abstract}

@@

\keywords{Security, Usability, Critical Infrastructure}

>>>>

\begin{document}
\title{Usable Security in Virtual Power Plants}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as  \texttt{acmart.pdf} document}

@@

\begin{abstract}
Automation of systems requires users to be less involved in system control. During situations when the user must interface with the system by themselves, the technology available must assist the user to complete their task and must not be a hindrance. Therefore, it is necessary to make the system more usable. Usability is often overlooked in favour of primary system goals, hence the lack of advancement in the usability drive. There exists no concrete framework to assess usability of a system, since most existing approaches focus on user feedback and neglect system optimization. In this study, usability is described in context of security in virtual power plants. A usability framework was established for authentication mechanisms. It was determined that usability arises by optimizing system factors that relate to usability standards with the crucial addition of user preferences. Additionally, the approach can be applied to any target system to assess usability.
\end{abstract}

@@

\keywords{Security, Usability, Virtual Power Plants}
